### 2021-04-17 paper/maxdet.tex
Explicit form of M^{-1} added.

\subsection{The completion}
With the result from the last section we have a way to proceed. We can look at the correlation matrix for the elements in $I$ that we obtain when we condition on the elements in $\gamma=\alpha\cap\beta$. This matrix is given by the Schur complement
\begin{equation}
	M/M[\sigma].
\end{equation}
We can use equation (\ref{eqn.corrmatrix}) to write
\begin{align}
	M/M[\sigma] & = M/E \\
	& = \begin{pmatrix}
		C - D E^{-1} D^T & W - DE^{-1}F \\
		W^T - F^TE^{-1}D^T & G - F^TE^{-1}F
		\end{pmatrix}.
\end{align}
A special choice for $W$ now presents itself. If we choose 
\begin{equation}\label{eqn.choice}
	W = DE^{-1}F 
\end{equation}
the off-diagonal matrices vanish and the matrix becomes block-diagonal. We can even interpret the remaining blocks. We note that 
\begin{align}
	M[\alpha]/M[\gamma] & = C - D E^{-1} D^T \\
	M[\beta]/M[\gamma] & = G - F^TE^{-1}F.
\end{align}
Again, using the result from the previous section, we see that the remaining blocks give the correlation matrix for $\alpha$ and $\beta$ respectively, when we condition on $\gamma$. The block-diagonal form in equation (\ref{eqn.choice}) says that the variables $\alpha$ conditioned on $\gamma$ are independent from the variables $\beta$ conditioned on $\gamma$. If $f$ is the corresponding density function we have
\begin{equation}
	f(x_{I-\gamma} \vert \gamma ) = f(x_{\alpha-\gamma} \vert \gamma )f(x_{\beta-\gamma} \vert \gamma ).
\end{equation}
Given that $\gamma$ is shared by both $\alpha$ and $\beta$ this is the most independence that we can hope for.

@@

\subsection{Zeroes \& the inverse matrix}
To state the next characterization of $W$ it is convenient to choose a different order for the rows and columns of $M$. Let us introduce the matrices
\begin{align}
	A = M[I-\gamma] \\
	B = M[\gamma, I - \gamma]
\end{align}
and write
\begin{equation}
	M = \begin{pmatrix}
		E & B \\
		B^T & A
	\end{pmatrix}.
\end{equation}
Babachiewicz \cite{horn} found a way to write the inverse of $M$ in terms of the Schur complement:
\begin{equation}
	M^{-1} = \begin{pmatrix}
		E^{-1} + E^{-1}B(M/E)^{-1}B^TE^{-1} & - E^{-1}B (M/E)^{-1} \\
		-(M/E)^{-1}B^TE^{-1} & (M/E)^{-1}
	\end{pmatrix}.
\end{equation}
With our choice of $W$, $M/E$ is block-diagonal. It follows that $(M/E)^{-1}$ is also block-diagonal:
\begin{equation}
	(M/E)^{-1} = \begin{pmatrix}
		(M[\alpha]/M[\gamma])^{-1} & 0 \\
		0 & (M[\beta]/M[\gamma])^{-1}
	\end{pmatrix}
\end{equation}
We see that the inverse of $M$ has zeroes in exactly the places where the undetermined matrix $W$ used to be.

>>>>

\subsection{The completion}
With the result from the last section we have a way to proceed. We can look at the correlation matrix for the elements in $I$ that we obtain when we condition on the elements in $\gamma=\alpha\cap\beta$. This matrix is given by the Schur complement
\begin{equation}
	M/M[\gamma].
\end{equation}
We can use equation (\ref{eqn.corrmatrix}) to write
\begin{align}
	M/M[\gamma] & = M/E \\
	& = \begin{pmatrix}
		C - D E^{-1} D^T & W - DE^{-1}F \\
		W^T - F^TE^{-1}D^T & G - F^TE^{-1}F
		\end{pmatrix}.
\end{align}
A special choice for $W$ now presents itself. If we choose 
\begin{equation}\label{eqn.choice}
	W = DE^{-1}F 
\end{equation}
the off-diagonal matrices vanish and the matrix becomes block-diagonal. We can even interpret the remaining blocks. We note that 
\begin{align}
	M[\alpha]/M[\gamma] & = C - D E^{-1} D^T \\
	M[\beta]/M[\gamma] & = G - F^TE^{-1}F.
\end{align}
Again, using the result from the previous section, we see that the remaining blocks give the correlation matrix for $\alpha$ and $\beta$ respectively, when we condition on $\gamma$. The block-diagonal form in equation (\ref{eqn.choice}) says that the variables $\alpha$ conditioned on $\gamma$ are independent from the variables $\beta$ conditioned on $\gamma$. If $f$ is the corresponding density function we have
\begin{equation}
	f(x_{I-\gamma} \vert \gamma ) = f(x_{\alpha-\gamma} \vert \gamma )f(x_{\beta-\gamma} \vert \gamma ).
\end{equation}
Given that $\gamma$ is shared by both $\alpha$ and $\beta$ this is the most independence we can hope for.

@@

\subsection{Zeroes \& the inverse matrix}
A remarkable formula due to Babachiewicz \cite{horn} expresses the inverse of a matrix in terms of the Schur complement. For a matrix
\begin{equation}
	\Sigma = \begin{pmatrix}
		\Sigma_{11} & \Sigma_{12} \\ 
		\Sigma_{21} & \Sigma_{22}
	\end{pmatrix}
\end{equation}
we have
\begin{equation}
	\Sigma^{-1} = \begin{pmatrix}
		\Sigma_{11}^{-1} + \Sigma_{11}^{-1}\Sigma_{12}(\Sigma/\Sigma_{11})^{-1}\Sigma_{21}\Sigma_{11}^{-1} &-\Sigma_{11}^{-1} \Sigma_{12} (\Sigma/\Sigma_{11})^{-1} \\ 
		-(\Sigma/\Sigma_{11})^{-1}\Sigma_{21}\Sigma_{11}^{-1} & (\Sigma/\Sigma_{11})^{-1}
	\end{pmatrix}.
\end{equation}
This formula has the remarkable property that only the inverses 
\begin{equation}
	\Sigma_{11}^{-1} \text{\ and\ } (\Sigma/\Sigma_{11})^{-1}
\end{equation}
appear in it. With our choice of $W$ in equation (\ref{eqn.choice}) the Schur complement $M/E$ is block diagonal. This means that also its inverse is block diagonal. Indeed, we have
\begin{equation}
	(M/E)^{-1} = \begin{pmatrix}
		(M[\alpha]/E)^{-1} & 0 \\
		0 & (M[\beta]/E)^{-1}
	\end{pmatrix}.
\end{equation}
This allows us to write the inverse of $M$ explicitly:
\begin{equation}
	M^{-1} = \begin{pmatrix}
		(M[\alpha]/E)^{-1} & -(M[\alpha]/E)^{-1} D E^{-1} & 0 \\
		- E^{-1} D^T (M[\alpha]/E)^{-1} & \Xi & - E^{-1} F (M[\beta]/E)^{-1} \\
		0 & - (M[\beta]/E)^{-1} F^T E^{-1} & (M[\beta]/E)^{-1}
	\end{pmatrix},
\end{equation}
with
\begin{equation}
	\Xi = E^{-1} + E^{-1}\left(D^T(M[\alpha]/E)^{-1}D + F (M[\beta]/E)^{-1} F^T\right)E^{-1}.
\end{equation}
We see that the inverse of $M$ has zeroes in exactly those places where the undetermined matrix $W$ used to be.
